### 2023-01-19 manuscript.Rmd
added to intro on research software engineering and importance of software in science

Based on four basic principles of a more responsible research assessment in academic hiring and promotion processes [@schonbrodt2022responsible], @gartner2022responsible suggest a specific implementation to broaden the range of what constitutes research contributions. Gaertner et al. provide evaluation schemes for published manuscripts, published datasets, and software contributions. Here, we specifically comment on the proposed evaluation scheme for research software contributions (Table 3). In the following, we comment on the dimensions metrics, lines of code, software engineering, impact, peer-review, usability.

>>>>

Based on four basic principles of a more responsible research assessment in academic hiring and promotion processes [@schonbrodt2022responsible], @gartner2022responsible suggest a specific implementation to broaden the range of what constitutes research contributions. Gaertner et al. provide evaluation schemes for published manuscripts, published datasets, and software contributions.
Why are research software contributions important academic contributions? We would like to respond with a quote from the Science Code Manifesto (http://sciencecodemanifesto.org/):
"Software is an essential research product, and the effort to produce, maintain, adapt, and 
curate code must be recognized."
and
"Software is a cornerstone of science. Without software, twenty-first century science would be impossible."
Yet, despite the heavy reliance on computational infrastructure, the current academic infrastructure does not adequately incentivice good software engineering practice that we would expect from a research software engineer [@baxter2012research]. 
 Here, we specifically comment on the proposed evaluation scheme for research software contributions (Table 3 of @gartner2022responsible). We comment on the dimensions metrics, lines of code, software engineering, impact, peer-review, usability.
